Untitled

### 2024-08-26 code/manuscript_analysis.Rmd
NBew Table 1

         crc.rate = crc.rate * 100, 
         pap.rate = pap.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         htn.rate = htn.rate * 100, 
         dm.rate = dm.rate * 100) %>% 
  #mutate(Qcomp = (crc.rate + pap.rate + adultbmi.rate + childbmi.rate) / 4) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Total, Qcomp, Altman, #MCD:COM, 
         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
         #Liquidity:NetWorth, 
         Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman)

@@

df.core %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(Total:Altman) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Total:Altman) %>% 
  mutate(value = round(value, 2)) %>% 
  filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.core, NiceName = c("Total","Quality Composite","Altman's Z")) %>% 
   select(NiceName, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
  mutate(Estimate = round(Estimate, 2), 
         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
  rename(Outcome = NiceName) %>% 
  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))

p0 <- ggarrange(
  event_study(data = df.core, 
  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients"), 
event_study(data = df.core, 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
event_study(data = df.core, 
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, ncol = 1 ) 
p0

summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Total ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Qcomp ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Altman ~ Treated*year.rel))$coeff[4,]

@@

p0 <- ggarrange(
  event_study(data = df.core, 
  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients"), 
event_study(data = df.core, 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
event_study(data = df.core, 
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, ncol = 3 ) 
p0

@@

label1 <- 'beta[pooled] == "2.24**"'
label2 <- 'beta[pooled] == "-0.21**"'

p0.simple <- ggarrange(
event_study(data = df.core, 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points") +
  annotate("text", x=2, y=-2.2, label= label1, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold")), 
event_study(data = df.core, 
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Altman's Z Score") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units") +
  annotate("text", x=2, y=0.4, label= label2, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold")), common.legend = TRUE, ncol = 2, legend = F) 
p0.simple

>>>>

         crc.rate = crc.rate * 100, 
         pap.rate = pap.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         htn.rate = htn.rate * 100, 
         dm.rate = dm.rate * 100, 
         logPatsPerStaff = log(Total / Staff), 
         logPatsPerStaff = ifelse(log(Total / Staff) > quantile(logPatsPerStaff, 0.975, na.rm = T), quantile(logPatsPerStaff, 0.975, na.rm = T), 
                                  ifelse(log(Total / Staff) < quantile(logPatsPerStaff, 0.025, na.rm = T), quantile(logPatsPerStaff, 0.025, na.rm = T), log(Total / Staff)))) %>% 
  #mutate(Qcomp = (crc.rate + pap.rate + adultbmi.rate + childbmi.rate) / 4) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Qcomp, Altman, logPatsPerStaff, #MCD:COM, 
         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
         #Liquidity:NetWorth, 
         Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman)

@@

df.core %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(Qcomp:logPatsPerStaff) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Qcomp:logPatsPerStaff) %>% 
  mutate(value = round(value, 2)) %>% 
  filter(name %in% c("Qcomp", "Altman","logPatsPerStaff")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.core, NiceName = c("Quality of Care","Financial Resilience","Operational Efficiency")) %>% 
   select(NiceName, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
  mutate(Estimate = round(Estimate, 2), 
         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
  rename(Outcome = NiceName) %>% 
  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))

p0 <- ggarrange(
  event_study(data = df.core, 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
event_study(data = df.core, 
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), 
event_study(data = df.core, 
  yname = "logPatsPerStaff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("log Ratio Patients-to-Staff"), common.legend = TRUE, ncol = 1 ) 
p0

summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Qcomp ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)), Altman ~ Treated*year.rel))$coeff[4,]
summary(lm(data = df.core %>% filter(!is.na(Tx) & year.rel < 0) %>% mutate(Treated = ifelse(Att > 0, 1, 0)) %>% filter(!is.infinite(logPatsPerStaff)), logPatsPerStaff ~ Treated*year.rel))$coeff[4,]

@@

p0 <- ggarrange(
  event_study(data = df.core, 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients"), 
event_study(data = df.core, 
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), 
event_study(data = df.core, 
  yname = "logPatsPerStaff", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
  #facet_wrap(~V1, scales = "free_y", ncol = 3) +
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("log Ratio Patients-to-Staff"), common.legend = TRUE, ncol = 3 ) 
p0

@@

# label1 <- 'beta[pooled] == "2.24**"'
# label2 <- 'beta[pooled] == "-0.21**"'
# 
# p0.simple <- ggarrange(
# event_study(data = df.core, 
#   yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
#   filter(abs(term) <= 5) %>% 
#   filter(estimator == "Gardner (2021)") %>% 
#   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
#   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6)+ theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points") +
#   annotate("text", x=2, y=-2.2, label= label1, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
#         axis.title=element_text(size=14,face="bold")), 
# event_study(data = df.core, 
#   yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
#   filter(abs(term) <= 5) %>% 
#   filter(estimator == "Gardner (2021)") %>% 
#   ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9), color = 'goldenrod', size = 3) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.25, position = position_dodge(0.9), color = 'goldenrod', size = 0.8)  +
#   #facet_wrap(~V1, scales = "free_y", ncol = 3) +
#   theme_tufte_revised() + geom_vline(xintercept=-0.5, color="blue", linetype="dashed", alpha=.6) + theme(legend.position = "none", plot.title = element_text(size=18, face='bold')) + 
#   geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Altman's Z Score") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units") +
#   annotate("text", x=2, y=0.4, label= label2, parse = TRUE, size = unit(10, "pt"))+theme(axis.text=element_text(size=12),
#         axis.title=element_text(size=14,face="bold")), common.legend = TRUE, ncol = 2, legend = F) 
# p0.simple
